### 2017-11-16 Docs/Thesis/docs/appendix/appendixC.tex
3rd revision of the thesis text complete, apA and apB completed. Still have to finish apC and apD
updates on the thesis text

\section{CDFs distributions}

The trace \textit{bigflows-pcap} has a much higher inter packet rate, and a smaller dispersion. Weibull is the model chosen by AIC/BIC, and it is the second best on correlation and self-similarity (Exponential(Me) and Cauchy are the best respectively). Exponential(Me) chooses as the second preferable, has the closest to the original mean and standard deviation. Comparing the plots of the CDF function, the Weibull seams to express well both small and larger values of inter packet times, while Exponential(Me) is preciser on the mean values, as we can see at figure ~\ref{fig:aproximation-originalbigflows-cdf}.

>>>>

In this appendix, we include some plots made during the process of model validation from the chapter ~\ref{ch:modeling-evaluation}, not included in the final version of the text. They include:

\begin{itemize}

	\item CDF's distributions;

	\item QQPlots;

	\item Correlation;

	\item Hurst exponent;

	\item Mean inter-packet times;

	\item Standard deviation of inter-packet times;

\end{itemize}

### 2017-11-16 Docs/Thesis/docs/chapter3.tex
updates on the thesis text

SIMITAR works in four different states: as a sniffer, packet injector, client or server. 
When it working as a sniffer, is produces as output a Compact Trace Descriptor file. It may work over a \textit{pcap} file or an Ethernet interface.

>>>>

Each SIMITAR component works as a different application:

\begin{itemize}
	\item \texttt{sniffer-cli.py};
	\item \texttt{trace.db} (sqlite3 database);
	\item \texttt{trace-analyzer}.
	\item \texttt{simitar-gen} (traffic generator).
\end{itemize}

When it working as a sniffer, it strores data from the capture traffic in the sqlite3 database. It may work over a \textit{pcap} file or an Ethernet interface. Working as a trace a trace-analyzer, it receive the name of the trace as stored in the database, and creates a XML compact trace descriptor. The constants used in the modelling may be changed and provided as command line argument. If not, the default values will be used.

As a traffic generator it may work as a client or a server. Working as a server is necessary for tools that require establishing a connection before generate the traffic, such as Iperf and D-ITG. It will just work passivaly. Working as a client, is acts as a traffic emissor. Tools such as \textit{libtins} dos not require server operation the send the traffic.

### 2017-11-16 Docs/Thesis/docs/chapter5.tex
updates on the thesis text

As proof of concepts for our tool, we are going to use Mininet's emulated testbeds. We automate all these tests using scripts, so they are reproducible. They are responsible for running all the proposed tests in this chapter and perform the calculations. It includes:

@@

Each test is organized as a Python packege, responsible for tigger all the applications and other scripts. The parameters for each simulation can be configured by a \textit{config.py} file. Also the file \textit{README} provide a tutorial to run correctely each test. With all tools instaled, less then fifteen minutes is enought to stat runnin each test again.A complete specification of our scenario we show at the table ~\ref{tab:specifications}, including the hardware specificatins and the software versions.

@@

% Flows per second
\begin{figure}[ht!]
	\centering
	\subfloat[\textit{Iperf, single-hop, skype-pcap}]{
		\includegraphics[width=77mm]{figures/ch5/skype-iperf-FlowsPs.pdf}
		\label{fig:iperfFps}
	}
	\hspace{0mm}
	\subfloat[\textit{Iperf, tree, skype-pcap}]{
		\includegraphics[width=77mm]{figures/ch5/skype-tree-iperf-FlowsPs.pdf}
		\label{fig:iperftreeFps}
	}
	\hspace{0mm}
	\subfloat[\textit{libtins, single-hop, skype-pcap}]{
		\includegraphics[width=77mm]{figures/ch5/skype-tins-FlowsPs.pdf}
		\label{fig:tinsCdf}
	}
	\hspace{0mm}
	\subfloat[\textit{libtins, single-hop, langw10s-pcap}]{
		\includegraphics[width=77mm]{figures/ch5/lgw-tins-FlowsPs.pdf}
		\label{fig:tinsLgwFps}
	}
	\hspace{0mm}
	\caption{Flow per seconds}
	\label{fig:flows-ps}
\end{figure}
% Bandwidth
\begin{figure}[h!]
	\centering
	\subfloat[\textit{Iperf, single-hop, skype-pcap}]{
		\includegraphics[width=77mm]{figures/ch5/skype-iperf-Bandwidth.pdf}
		\label{fig:iperfBw}
	}
	\hspace{0mm}
	\subfloat[\textit{Iperf, tree, skype-pcap}]{
		\includegraphics[width=77mm]{figures/ch5/skype-tree-iperf-Bandwidth.pdf}
		\label{fig:iperftreeBw}
	}
	\hspace{0mm}
	\subfloat[\textit{libtins, single-hop, skype-pcap}]{
		\includegraphics[width=77mm]{figures/ch5/skype-tins-Bandwidth.pdf}
		\label{fig:tinsBw}
	}
	\hspace{0mm}
	\subfloat[\textit{libtins, single-hop, langw10s-pcap}]{
		\includegraphics[width=77mm]{figures/ch5/lgw-tins-Bandwidth.pdf}
		\label{fig:tinsLgwBw}
	}
	\hspace{0mm}
	\caption{Traces bandwidth.}
	\label{fig:flows-bandwidth}
\end{figure}
% Flow CDF
\begin{figure}[ht!]
	\centering
	\subfloat[\textit{Iperf, single-hop, skype-pcap}]{
		\includegraphics[width=77mm]{figures/ch5/skype-iperf-FlowCdf.pdf}
		\label{fig:iperfCdf}
	}
	\hspace{0mm}
	\subfloat[\textit{Iperf, tree, skype-pcap}]{
		\includegraphics[width=77mm]{figures/ch5/skype-tree-iperf-FlowCdf.pdf}
		\label{fig:iperftreeCdf}
	}
	\hspace{0mm}
	\subfloat[\textit{libtins, single-hop, skype-pcap}]{
		\includegraphics[width=77mm]{figures/ch5/skype-tins-FlowCdf.pdf}
		\label{fig:tinsCdf}
	}
	\hspace{0mm}
	\subfloat[\textit{libtins, single-hop, langw10s-pcap}]{
		\includegraphics[width=77mm]{figures/ch5/lgw-tins-FlowCdf.pdf}
		\label{fig:tinsLgwCdf}
	}
	\hspace{0mm}
	\caption{Flows cumulative distributions.}
	\label{fig:flows-cdf}
\end{figure}
% Wabelet
\begin{figure}[h!]
	\centering
	\subfloat[\textit{Iperf, single-hop, skype-pcap}]{
		\includegraphics[width=77mm]{figures/ch5/skype-iperf-WaveletMREA.pdf}
		\label{fig:iperfWaveletMREA}
	}
	\hspace{0mm}
	\subfloat[\textit{Iperf, tree, skype-pcap}]{
		\includegraphics[width=77mm]{figures/ch5/skype-tree-iperf-WaveletMREA.pdf}
		\label{fig:iperftreeWaveletMREA}
	}
	\hspace{0mm}
	\subfloat[\textit{libtins, single-hop, skype-pcap}]{
		\includegraphics[width=77mm]{figures/ch5/skype-tins-WaveletMREA.pdf}
		\label{fig:tinsWaveletMREA}
	}
	\hspace{0mm}
		\subfloat[\textit{libtins, single-hop, langw10s-pcap}]{
			\includegraphics[width=77mm]{figures/ch5/lgw-tins-WaveletMREA.pdf}
			\label{fig:tinsLgwWaveletMREA}
		}
		\hspace{0mm}
	\caption{Wavelet multiresolution energy analysis.}
	\label{fig:wavelet}
\end{figure}

We display our results in the figures ~\ref{fig:flows-ps} to ~\ref{fig:wavelet}, and in the table ~\ref{tab:results-summary}. As we can see in the figure ~\ref{fig:flows-bandwidth}, the generated traffics are not identical regarding bandwidth. But the synthetic and original both presents a fractal-like shape. In fact, the values of each  Hurst exponent of inter-packet times had an error smaller than 10\% compared to the original in every case.  The plot of flows per second seems much more accurate visually, since most of the peaks match.  We can analyze it precisely observing the cumulative flow distribution\ref{fig:flows-cdf}, where the results were almost identical on every plot. However, when SIMITAR is replicating the traffic of \textit{lgw10s-pcap} the number of flows per second decreases. It happens because of the methodology of traffic generation of the class \textit{TinsFlow} since it sends the packets of each flow as fast as possible. This behavior can be observed in the bandwidth plot as well since it is much larger in the first seconds.

%<<<<<<<<<<<<<<<<<<<<>>>>>>>>>>>>>>>>>>>>>>>>>

The best results achieved by SIMITAR were on the flow distribution characterization. On every experiment made, the cumulative distribution of flows was almost identical. The small imprecisions on the plots are expected and should result from threads and process concurrence of resources and imprecision on the sleep/wake signaling on the traffic generation side. Imprecisions on packet capture buffer may count as well since the operating system did the packet timing. This was our greatest achievement in our research. This result means that our method of flow scheduling and independent traffic generation were effective and efficient on replicating the original traffic. The actual number of flows was much larger when SIMITAR used Iperf and about the same amount but small when used libtins. This happens because Iperf establishes the connection to control the signaling and the traffic statistics in addition to the connection of the actual traffic. With libtins, the number is small because if an error happens when it is creating a flow, its execution is aborted.

On Wavelet multiresolution analysis of inter-packet times, the results have changed more in each case. The time resolution chosen was ten milliseconds, and it is represented in $\log_2$ scale. The actual time scale of each $j$ value is given by the equation:

@@

In the first case(figure ~\ref{fig:iperfWaveletMREA}), SIMITAR using Iperf in a single-hop scenario, on small time scales the energy level of the synthetic traffic remained almost constant, which indicates white-noise characteristics. The original skype traffic increased linearly, an indication of fractal shape. The synthetic trace started to increase at the time scale 5-6 (300-600 milliseconds). After this scale, the error between the curves become very small. One possible reason for this behavior is the fact that the constant which regulate the minimum burst time (\texttt{DataProcessor::m\_min\_on\_time}) is set to 100 milliseconds. For small time scales the traffic become similar to white noise since Iperf just emits traffic with constant bandwidth. For larger scales, it captures the same fractals patterns of the original trace. It also captures a periodicity pattern at the time-scale of 9 seconds. The authors of \cite{swing-paper} measured the same periodicity pattern. But on this trace, we observe some periodicity at 11 and 13 time-scales (20 and 80 seconds).

@@

The current implementation still has problems on accurately reproduce \textit{pcaps} with high bandwidth values and a larger number of flows. The major limitation is the time required to generate the compact trace descriptor.  The procedure is still mono-thread, and the linear regression procedure is not optimized. So, the time for processing a large pcap file with thousands of flows is still prohibitively high, spending dozens of hours on processing.

Using the first 10 seconds of the trace \textit{bigFlows-pcap}, on 10 seconds of operation, Iperf generated much fewer packets than the expected. It is an expected behavior since the operating system couldn't handle so much newer processes (one per flow) in such short time. On the other hand, the same drawback wasn't observed using libtins as traffic generator tool, since being a low-level API makes it much computationally cheaper.  In the figure ~\ref{fig:} we visualize the results of SIMITAR using \textit{libtins}. The flow's cumulative distribution was achieved a good result. But, the wavelet analysis curves still didn't match.

%\section{Current Limitations}
%
%To evaluate the Scalling profile of the traccic generator, we are usig the same validation used for Swing\cite{swing-paper}: multiresolution energy analysis.

>>>>

As proof of concepts for our tool, we are going to use Mininet's emulated testbeds. We automate all tests using scripts, so our experiments are are fully  reproducible. They are responsible for running all the proposed tests in this chapter and perform the calculations. It includes:

@@

Each test is organized as a Python packege, responsible for tigger all the applications and procedures. The parameters for each simulation can be configured by a \textit{config.py} file. The files \textit{README} on each packege, provide a tutorial to run correctely each test. With all tools instaled, less then fifteen minutes is enought for run each test again. A complete specification of our scenario we show at the table ~\ref{tab:specifications}, including the hardware specificatins and the software versions.

@@

% Bandwidth
\begin{figure}[h!]
	\centering
	\subfloat[\textit{Iperf, single-hop, skype-pcap}]{
		\includegraphics[width=77mm]{figures/ch5/skype-iperf-Bandwidth.pdf}
		\label{fig:iperfBw}
	}
	\hspace{0mm}
	\subfloat[\textit{Iperf, tree, skype-pcap}]{
		\includegraphics[width=77mm]{figures/ch5/skype-tree-iperf-Bandwidth.pdf}
		\label{fig:iperftreeBw}
	}
	\hspace{0mm}
	\subfloat[\textit{libtins, single-hop, skype-pcap}]{
		\includegraphics[width=77mm]{figures/ch5/skype-tins-Bandwidth.pdf}
		\label{fig:tinsBw}
	}
	\hspace{0mm}
	\subfloat[\textit{libtins, single-hop, langw10s-pcap}]{
		\includegraphics[width=77mm]{figures/ch5/lgw-tins-Bandwidth.pdf}
		\label{fig:tinsLgwBw}
	}
	\hspace{0mm}
	\caption{Traces bandwidth.}
	\label{fig:flows-bandwidth}
\end{figure}
% Flows per second
\begin{figure}[ht!]
	\centering
	\subfloat[\textit{Iperf, single-hop, skype-pcap}]{
		\includegraphics[width=77mm]{figures/ch5/skype-iperf-FlowsPs.pdf}
		\label{fig:iperfFps}
	}
	\hspace{0mm}
	\subfloat[\textit{Iperf, tree, skype-pcap}]{
		\includegraphics[width=77mm]{figures/ch5/skype-tree-iperf-FlowsPs.pdf}
		\label{fig:iperftreeFps}
	}
	\hspace{0mm}
	\subfloat[\textit{libtins, single-hop, skype-pcap}]{
		\includegraphics[width=77mm]{figures/ch5/skype-tins-FlowsPs.pdf}
		\label{fig:tinsCdf}
	}
	\hspace{0mm}
	\subfloat[\textit{libtins, single-hop, langw10s-pcap}]{
		\includegraphics[width=77mm]{figures/ch5/lgw-tins-FlowsPs.pdf}
		\label{fig:tinsLgwFps}
	}
	\hspace{0mm}
	\caption{Flow per seconds}
	\label{fig:flows-ps}
\end{figure}
% Flow CDF
\begin{figure}[ht!]
	\centering
	\subfloat[\textit{Iperf, single-hop, skype-pcap}]{
		\includegraphics[width=77mm]{figures/ch5/skype-iperf-FlowCdf.pdf}
		\label{fig:iperfCdf}
	}
	\hspace{0mm}
	\subfloat[\textit{Iperf, tree, skype-pcap}]{
		\includegraphics[width=77mm]{figures/ch5/skype-tree-iperf-FlowCdf.pdf}
		\label{fig:iperftreeCdf}
	}
	\hspace{0mm}
	\subfloat[\textit{libtins, single-hop, skype-pcap}]{
		\includegraphics[width=77mm]{figures/ch5/skype-tins-FlowCdf.pdf}
		\label{fig:tinsCdf}
	}
	\hspace{0mm}
	\subfloat[\textit{libtins, single-hop, langw10s-pcap}]{
		\includegraphics[width=77mm]{figures/ch5/lgw-tins-FlowCdf.pdf}
		\label{fig:tinsLgwCdf}
	}
	\hspace{0mm}
	\caption{Flows cumulative distributions.}
	\label{fig:flows-cdf}
\end{figure}
% Wabelet
\begin{figure}[h!]
	\centering
	\subfloat[\textit{Iperf, single-hop, skype-pcap}]{
		\includegraphics[width=77mm]{figures/ch5/skype-iperf-WaveletMREA.pdf}
		\label{fig:iperfWaveletMREA}
	}
	\hspace{0mm}
	\subfloat[\textit{Iperf, tree, skype-pcap}]{
		\includegraphics[width=77mm]{figures/ch5/skype-tree-iperf-WaveletMREA.pdf}
		\label{fig:iperftreeWaveletMREA}
	}
	\hspace{0mm}
	\subfloat[\textit{libtins, single-hop, skype-pcap}]{
		\includegraphics[width=77mm]{figures/ch5/skype-tins-WaveletMREA.pdf}
		\label{fig:tinsWaveletMREA}
	}
	\hspace{0mm}
		\subfloat[\textit{libtins, single-hop, langw10s-pcap}]{
			\includegraphics[width=77mm]{figures/ch5/lgw-tins-WaveletMREA.pdf}
			\label{fig:tinsLgwWaveletMREA}
		}
		\hspace{0mm}
	\caption{Wavelet multiresolution energy analysis.}
	\label{fig:wavelet}
\end{figure}

We display our results in the figures ~\ref{fig:flows-ps} to ~\ref{fig:wavelet}, and in the table ~\ref{tab:results-summary}, where the original and the synthetic traffics are compared. As we can see in the figure ~\ref{fig:flows-bandwidth}, the generated traffics are not identical regarding bandwidth, however both presents fractal-like shape. The Hurst exponent of inter-packet times in every case has an error smaller than 10\% compared to the original in every case. This result indicates that in fact, the fractal-level of each synthetic traffic is indeed similar to the original.

The plot of flows per second seems much more accurate visually since most of the peaks match.  Indeed, no visual lag between the plots. We can analyze it precisely observing the cumulative flow distribution\ref{fig:flows-cdf}, where the results were almost identical on every plot. However, when SIMITAR is replicating the traffic of \textit{lgw10s-pcap} the number of flows per second decreases. It happens because of the methodology of traffic generation of the class \textit{TinsFlow} since it sends the packets of each stream as fast as possible. So each flow occurrence is restricted to smaller intervals. This behavior can be observed as well in the bandwidth plot. It is much larger in the first seconds and small at the end.

The best results achieved by SIMITAR were on the flow distribution characterization. On every experiment made, the cumulative distribution of flows was almost identical. The small imprecisions on the plots are expected and should result from threads and process concurrence of resources and imprecision on the sleep/wake signaling on the traffic generation side. Imprecisions on packet capture buffer may count as well since the operating system did the packet timing. This was our most significant achievement in our research. This result means that our method of flow scheduling and independent traffic generation were effective and efficient on replicating the original traffic at the flow-level. The actual number of flows was much more significant when SIMITAR used Iperf and about the same amount but little small when used libtins. This discrepancy happens with Iperf because it establishes additional connections to control the signaling and traffic statistics.  So, this more substantial number of flows comes from accounting, not just the traffic connections, but also with the signaling as well.  With libtins, the number of flows is small, because, if it fails to create a new traffic flow, this flows generation execution is aborted.

On Wavelet multiresolution analysis of inter-packet times, the results have changed more in each case. The time resolution chosen was ten milliseconds, and it is represented in $\log_2$ scale. The actual time pf each time-scale $j$ value is given by the equation:

@@

In the first case (figure ~\ref{fig:iperfWaveletMREA}), SIMITAR using Iperf in a single-hop scenario, on small time scales the energy level of the synthetic traffic remained almost constant, which indicates white-noise characteristics. The original skype traffic increased linearly, an indication of fractal shape. The synthetic trace started to increase at the time scale 5-6 (300-600 milliseconds). After this scale, the error between the curves become very small. One possible reason for this behavior is the fact that the constant which regulate the minimum burst time (\texttt{DataProcessor::m\_min\_on\_time}) is set to 100 milliseconds. For small time scales the traffic become similar to white noise since Iperf just emits traffic with constant bandwidth. For larger scales, it captures the same fractals patterns of the original trace. It also captures a periodicity pattern at the time-scale of 9 seconds. The authors of \cite{swing-paper} measured the same periodicity pattern. But on this trace, we observe some periodicity at 11 and 13 time-scales (20 and 80 seconds).

@@

The current implementation still has problems on accurately reproduce \textit{pcaps} with high bandwidth values and a more substantial number of flows. The primary limitation is the time required to generate the trace descriptor.  The procedure is still mono-thread, and the linear regression procedure is not optimized. Although creating a trace descriptor of a small pcap file is fast, the time for processing large pcap file with thousands of flows is still prohibitively high, spending dozens of hours.

Using the first 10 seconds of the trace \textit{bigFlows-pcap}, on 10 seconds of operation, Iperf generated much fewer packets than the expected. It is an expected behavior since the operating system couldn't handle so much newer processes (one per flow) in such short time. On the other hand, the same drawback wasn't observed using libtins as traffic generator tool, since being a low-level API makes it much computationally cheaper.  Some others unexpected behavior must have a more in-depth investigation, such as libtins generating more packets than expected for \textit{skype-pcap}, but not for \textit{lgw10s-pcap}, and why the creation of some flows fail, and how to fix it if possible.

Another promising possible investigation is what traffic each tool can better represent. In terms of number of flows and packets, bandwidth and for larger \textit{pcaps}, \textit{libtins} is a best option. But Iperf has presented a better performance replicating scaling characteristics of applications.

### 2017-11-16 Docs/Thesis/docs/chapter6.tex
updates on thesis text
updates on the thesis text

In this section we present some ideas for future works and implementation for SIMITAR. On the first section "Improoving results", we suggest approaches for improving the current results. They include calibration of some constants, finer controll of packet injection, and performance improovments.

\subsection{Improoving results}

@@

To improve our results, the first approach is performing a deeper study on calibrating each tool, to achieve the best results possible. We can do this first adjusting some constants used by our algorithms. Some of these values will change the performance not for all but on tools that support stochastic functions for inter packet times. They are:

\begin{itemize}
	\item \texttt{DataProcessor::minimumAmountOfPackets}: SIMITAR only estimates stochastic models for inter-packet times if the number of flow packets is larger than this value. If it is smaller, we use only the constant model, for two reasons. First, because with a small sample, the accuracy estimate stochastic model is poor. Second, because we avoid the parameterization process, which can be costly in the case of linear regression. Its value today is set to 30.increasing this value, we may achieve a more reasonable performance for individual flows. 
	\item \texttt{DataProcessor::min\_time}: smallest time considered for inter-packet times. We use this value to avoid inter-packet times equals to zero due to the sniffer resolution. In that case, some of our procedures would diverge. It can change the fitting accuracy. Today, this value is $5e-8$. 
\end{itemize}

The modification of others  constants or approaches may change the performance for any type of underlying tool or API. They are:

@@

% Para extensão do trafego gerado, é necessário um estudo da melhor calibração para cada ferramente, como o D-ITG, Iperf, Libtins, o que pode melhorar os resultados

\subsubsection{SIMITAR as a Packet Injector}

This proposed functionality is still under implementation, and we are using Libtins API \footnote{\href{http://libtins.github.io/}{http://libtins.github.io/}}. It enables packet crafting and injection at a reasonable performance, and provide support for many protocols. It is not threaded safe, so will require some cars, such as the use of mutexes. But will enable a finer control of packet header contents, packet sizes, inter-packet times and a number of packets sent. In that way, we expect to achieve better results in terms of realism.

\begin{figure}[!ht]
	\centering
	\includegraphics[height=2.0in]{figures/ch6/libtins-flow}
	\caption{Expansion of SIMITAR using Libtins for traffic generation}
	\label{fig:libtins-flow}
\end{figure}

@@

\subsubsection{Thread Menager}

Instead of each flow's thread control individually sleep and wake times, a better approach would be a separated thread control and manage all the other threads' life-cycle operation. This approach can increase the timing accuracy for flows and \textit{files}.

% \subsubsection{Improving DataProcessor Performance}

% Melhorar os algoritimos adicionando técnicas adicionais de modelagem, como condição de parada para o algoritimo gradient descendent, stochastic gradient descendent, entre outros

@@

	\item \textbf{Use OpenDayLight REST API for data collection}: Another different approach for data collection could be the use the OpenDayLight REST API to collect data from an SDN OpenFlow switches, instead of a using a Sniffer. Through REST API is possible to extract many statistics from nodes, hosts, and ports, such active flows, the number of packets matched per flows, packet drops, and so on. But, different features would be measured,  and a new model for traffic generation would be needed. On the other hand, we could reuse many procedures implemented.

>>>>

In this section we discuss some ideas for future works and implementation for SIMITAR. On the first section "Improoving results", we suggest approaches to get better results. They include calibration of some constants, finer controll of packet injection, and performance improovments.

\subsection{Improoving performance}

The major issue of SIMITAR now is optimizing data processing for creating the compact trace descriptor. In the current implementation, the linear regression is mono-thread, and the stop criteria are just the number of iterations. Parallel processing, and creating stop criteria based on convergence should increase the processing performance.

On the traffic generation, currently, the threads for all flows are being instantiated once the traffic generations start. A smarter traffic generation, where each thread is instantiated when the traffic is active and dies when it is inactive should reduce the overhead for \textit{pcap} files with a large number of flows. For traffic with a massive amount of flows, a methodology for merging them should reduce overheads and enable replication of traffic with a larger bandwidth.

Finally, the current implementation using \textit{libtins} to generate the packets does not model inter-packet times. To avoid processing overheads on calculating random numbers, these values may be calculated before the actual traffic generation, and then be used. By this approach, the scaling characteristics of the traffic generated by libtins should improve, and be closer to the original traffic.

@@

To improve our results, the first approach is performing a deeper study on calibrating each tool, to achieve the best results possible. We can do this first adjusting some constants used by our algorithms. Some of these values will change the performance on tools that supports stochastic functions for inter packet times. They are:

\begin{itemize}
	\item \texttt{DataProcessor::minimumAmountOfPackets}: SIMITAR only estimates stochastic models for inter-packet times if the number of flow packets is larger than this value. If it is smaller, we use only the constant model, for two reasons. First, because with a small sample, the accuracy estimate stochastic model is poor. Second, because we avoid the parameterization process, which can be costly in the case of linear regression. Its value today is set to 30. Increasing this value, we may achieve a more reasonable performance for individual flows. 
	\item \texttt{DataProcessor::min\_time}: smallest time considered for inter-packet times. We use this value to avoid inter-packet times equals to zero due to the sniffer resolution. In that case, some of our procedures would diverge. It can change the fitting accuracy. Today, this value is $5e-8$. 
\end{itemize}

The modification of others  constants or approaches may change the performance for any tool or API. They are:

@@

@@

@@

	%\item \textbf{Use OpenDayLight REST API for data collection}: Another different approach for data collection could be the use the OpenDayLight REST API to collect data from an SDN OpenFlow switches, instead of a using a Sniffer. Through REST API is possible to extract many statistics from nodes, hosts, and ports, such active flows, the number of packets matched per flows, packet drops, and so on. But, different features would be measured,  and a new model for traffic generation would be needed. On the other hand, we could reuse many procedures implemented.
